Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-25 ms.tex
added an example fit for 2016-06-12.
added additional fits.

\begin{deluxetable}{lr}
\tablecaption{List of observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Comment} \\
\colhead{UT} & \\
 }
\startdata
2016-06-10 & Clouds \\
2016-06-12 & Clear \\
2016-06-14 & Clear \\
2016-07-12 & Clear \\
2016-07-14 & Mostly clear \\
2016-07-16 & Clear \\
\enddata
\tablenotetext{}{Summary of observations and conditions in this work.}
\end{deluxetable}

@@

>>>>

\begin{deluxetable}{lrr}
\tablecaption{List of observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Comment} \\
\colhead{UT} & \\
\colhead{Amplitude} & \\
 }
\startdata
2016-06-10 & Clouds	& \\
2016-06-12 & Clear 		& \\
2016-06-14 & Clear 		&\\
2016-07-12 & Clear 		&\\
2016-07-14 & Mostly clear	& \\
2016-07-16 & Clear 		& \\
\enddata
\tablenotetext{}{Summary of observations and conditions in this work.}
\end{deluxetable}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=0.9\textwidth]{images/tser_fits/best_fit_all.pdf}
\caption{Best-fit for all nights.}\label{fig:fitAll}
\end{centering}
\end{figure*}
